---
title: "I-CAH UK practice"
author: "R.Welch"
date: "2025-02-04"
output: html_document
---

---
title: "The perfect processed clean I-CAH-UK data"
author: "R.Welch"
date: "2025-01-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

libraries
```{r : reading libraries, include= FALSE}
packages <- c("tidyverse", "readxl", "dplyr", "magrittr", "mixtools", "emmeans", "readr","data.table", "lubridate", "ggplot2", "magrittr", "skimr", "ggstatsplot","summarytools", "knitr", "here", "ggthemes", "ggthemes", "Amelia", "tidyr", "naniar", "stringr")

lapply(packages, library, character.only = TRUE)
```

```{r : reading in data}
participants <- read.csv("C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/data/STUDY 202203_NK data extraction 10.3.24.csv", header=T, na.strings="")

ae <- read.csv("C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/data/AE with cname, dob, visitdate UK 12.3.24.csv", header=T, na.strings="")

medication <- read.csv("C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/data/Meds with cname, dob, visitdate UK 12.3.24.csv", header=T, na.strings="NULL")

fludro <- read.csv("C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/data/Fludro with cname, dob, visitdate UK 12.3.24.csv", header=T, na.strings="NULL")

labs <- read.csv("C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/data/Labs with cname, dob, visitdate UK 12.3.24.csv", header=T, na.strings="NULL")
```

*********************************
*********************************
------Removing duplicates------

Making unique identifier for each assessment by combining co-id and assessment date.
```{r : making new unique identifier}
participants$coid_asse_date <- paste(participants$Register.ID...Record, participants$Date...CAH.Longitudinal.Data)
```

Checking for any duplicate entries (i.e.: any duplicates in the newly made unique identifier).
'list of duplicates frame' gives output of duplicate candidates
```{r : checking for duplicates}
duplicates <- freq(participants$coid_asse_date)
duplicatesframe <- as.data.frame(duplicates)
duplicatesframe <- rownames_to_column(duplicatesframe, var="idvisitdate")
```

Now to remove any non-duplicates in 'duplicatesframe' to show us what the actual duplicates are and how many times they've been duplicated
```{r : isolating duplicate occurances, include= FALSE}
duplicatesframe <- duplicatesframe[duplicatesframe$idvisitdate != c("Total", "<NA>"),]
duplicatesframe <- duplicatesframe[-c(3:6)]

duplicateassessments <- duplicatesframe %>%
  filter(Freq>1)
```

Make a new vector to use as list of duplicate entries to remove from participants dataframe and then remove duplicated entries from participants dataframe with a subset.
Because there's no way of knowing which duplicate entry is the correct one, all duplicates are removed.
```{r : removing duplicates, include=FALSE}
idvisitstoremove <- duplicateassessments$idvisitdate

participantsnoduplicates <- subset(participants, !coid_asse_date %in% idvisitstoremove)

freqcheck <- as.data.frame(freq(participantsnoduplicates$coid_asse_date))
freqcheck <- rownames_to_column(freqcheck, var="idvisitdate")
freqcheck <- freqcheck[freqcheck$idvisitdate != c("Total", "<NA>"),]
# freqcheck
```

Making a dataframe of the removed duplicate assessment entries
```{r : removed duplicates}
toremove <- duplicateassessments$idvisitdate
removedrecords <- subset(participants, coid_asse_date %in% toremove)

write.csv(removedrecords, file = "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/removedrecords.csv", row.names = F, na = "")
```

Because I've removed all duplicate assessment entries, we might have lost participant/s if their only entry is one of these removed duplicates.
This will show which participants, if any, have been lost.
We need to split apart the idvisitdate to get the CO.IDs isolated
```{r : identifying lost participants}
duplicateassessments$id <- sapply(strsplit(duplicateassessments$idvisitdate," "), `[`, 1)
duplicateassessments$visitdate<- sapply(strsplit(duplicateassessments$idvisitdate," "), `[`, 2)

toremovelostparticipants <- participantsnoduplicates$Register.ID...Record

lostparticipants <- NA
lostparticipants <- subset(participants, !Register.ID...Record %in% toremovelostparticipants)

write.csv(lostparticipants, file = "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/lostparticipants.csv", row.names = F, na = "")

print("Due to duplications during data entry, we have lost")
n_unique(lostparticipants$Register.ID...Record)
print("participants (because their only 'contributions' to the database have been removed)")
```

```{r : making participantsnoduplicates}
idvisitstoremove <- duplicateassessments$idvisitdate

participantsnoduplicates <- subset(participants, !coid_asse_date %in% idvisitstoremove)

freqcheck <- as.data.frame(freq(participantsnoduplicates$coid_asse_date))
freqcheck <- rownames_to_column(freqcheck, var="idvisitdate")
freqcheck <- freqcheck[freqcheck$idvisitdate != c("Total", "<NA>"),]

write.csv(participantsnoduplicates, file = "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/participantsnoduplicates.csv", row.names = F, na = "")
```

*************************************
Visit statistics
***********************************

This chunk groups the records by separate patients, and tells us how many visits they had. Then we take that long dataframe that has told us how many visits each of them have, and create some summary statistics to give us an idea of how many patients we have, and how many visits we have data for. 
```{r : visit stats}
numbervisits <- participantsnoduplicates %>%
  group_by(Register.ID...Record) %>%
  summarise(n=n())

numbervisitsstats <- numbervisits %>%
  summarise(numberpatients =n(),
            meanvisits=mean(n, na.rm = TRUE),
            medianvisits=median(n, na.rm = TRUE),
            sdvisits=sd(n, na.rm = TRUE),
            minvisits=min(n, na.rm = TRUE),
            maxvisits=max(n, na.rm = TRUE))
```


```{r : visits per centre}
centrevisits <- participantsnoduplicates %>%
  group_by(Centre.Name...Centre, Country...Centre) %>%
  summarise(number_of_visits = n())

write.csv(centrevisits, "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/centrevisits.csv", row.names = F, na = "")

patientspercentre <- participantsnoduplicates %>%
  group_by(Centre.Name...Centre) %>%
  summarise(number_of_patients = n_unique(Register.ID...Record))

write.csv(patientspercentre, "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/patientspercentre.csv", row.names = F, na = "")

centreparticipation <- left_join(centrevisits, patientspercentre, by="Centre.Name...Centre")

write.csv(centreparticipation, "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/centreparticipation.csv", row.names = F, na = "")

countryvisits <- participantsnoduplicates %>%
  group_by(Country...Centre) %>%
  summarise(number_of_centres = n_unique(Centre.Name...Centre),
            number_of_visits = n(),
            number_of_patients = n_unique(Register.ID...Record))

write.csv(countryvisits, "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/countryparticipation.csv", row.names = F, na = "")
```

***********************
Calculating total medication doses
************************

```{r : medication per visit}
totalmedicationcalculation <- medication %>%
  group_by(assessment_id) %>%
  summarise(total_dose = sum(dose, na.rm = TRUE))

totalmedication <- left_join(medication, totalmedicationcalculation, by = "assessment_id")

singletotalmedication <- totalmedication %>%
  distinct(assessment_id, .keep_all = TRUE)
singletotalmedication <- subset(singletotalmedication,
                                select = -c(dose, time, note))
# singletotalmedication is med frame with one row per assessment with the total med dose included
```


```{r : medication visits}
medication_details <- medication %>%
  group_by(assessment_id) %>%
  summarise(n = n())

numbervisitsstats$visits_with_med_data <- medication_details %>%
  summarise(n = n())

numbervisitsstats$visits_with_lab_data <- n_unique(labs$assessment_id)

write.csv(numbervisitsstats, file = "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/numbervisitsstats.csv", row.names = F, na = "")
```

let's next combine the  AE1, medication1, fludro1 and labs1 tables with the all visits
```{r : joining meds and ae}
meds <- left_join(singletotalmedication, fludro, by = c("record_id", "assessment_id", "assessment_date"))
medsandae <- left_join(meds, ae, by = c("record_id", "assessment_id", "assessment_date"))

#make unique identifier in medsandae
medsandae$coid_asse_date <- paste(medsandae$record_id, medsandae$assessment_date)

# removing all duplicated entries (based on coid_asse_date)
medsandae_duplicates <- medsandae[duplicated(medsandae$coid_asse_date),]

medsandae_entries_to_remove <- medsandae_duplicates$coid_asse_date
medsandae <- subset(medsandae, !coid_asse_date %in% medsandae_entries_to_remove)

# med_duplicates_check should now be empty
medsandae_duplicates_check <- medsandae[duplicated(medsandae$coid_asse_date),]

write.csv(medsandae, file = "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/medsandae.csv", row.names = F, na = "")
```

***********************
Medication frame
************************
Let's start by cleaning medication data frame (units, typos, standardised doses)
Create unique identifier of coid_asse_date
```{r : medication data frames}
medication_clean <- medication
medication_clean$coid_asse_date <- paste(medication_clean$record_id, medication_clean$assessment_date)
medication_clean$coid_asse_id <- paste(medication_clean$record_id, medication_clean$assessment_id)

# note column is always empty / "NULL", so remove it
table(medication_clean$note)
medication_clean$note <- NULL

# assessment date as date type, not character
medication_clean$assessment_date <- 
  as.Date(medication_clean$assessment_date, format="%d/%m/%Y")

# time as time not numeric
medication_clean$hours_through_day <- as.numeric(medication_clean$time / 3600)
medication_clean$hours_through_day <- round(medication_clean$hours_through_day, digits = 0)

medication_clean$hours_through_day <-
  ifelse(medication_clean$hours_through_day != 0,
         as.numeric(medication_clean$hours_through_day),
         NA)
```

Now let's check what units have been used to see if we need to standardise any...
Assuming that NULL units are also mg.

```{r}
medication_clean <- medication_clean[order(medication_clean$assessment_id, medication_clean$time),]

table(medication_clean$unit)
# if mcg has been used, according to ^, then the associated dose value needs to be changed/standardised.

# these are the records using mcg as units
units_mcg <- subset(medication_clean, unit == "mcg")
units_mcg$dose

# let's correct the doses of mcg records
medication_clean$dose <-
  ifelse(medication_clean$unit == "mcg",
         as.numeric(medication_clean$dose) * 1000,
         as.numeric(medication_clean$dose))

units_mcg$dose

medication_clean$dose <-
  ifelse(medication_clean$unit=="mcg" &
         medication_clean$medicine=="dexamethasone",
         as.numeric(medication_clean$dose) / 1000 ,
         as.numeric(medication_clean$dose))

#remember, we need to correct the dose if the preparation is unknown, otherwise it will go to NA
medication_clean$dose <-
  ifelse(is.na(medication_clean$medicine),
         as.numeric(medication_clean$dose),
         as.numeric(medication_clean$dose))

units_mcg$dose

# update units
medication_clean$unit <-
  ifelse(medication_clean$unit == "mcg",
         "mg",
         medication_clean$unit)

table(medication_clean$unit)
```

```{r : check units for dexamethasone - DO SEPARATELY FOR EACH ANALYSIS}
#FOR 12.3.24 DATA, NO DEXAMETHASONE WAS IN DATASET SO THIS SECTION HAS BEEN SKIPPED.

# dex_subset <- subset(medication_clean, medicine == "dexamethasone")
# max(dex_subset$dose, na.rm = T)
# # ^ shows values of 250 (i.e OVER 10) which is TOO HIGH, therefore it's likely that these values are indeed in mcg, therefore we need to manually change these.
# 
# dex_HIGH_values <- subset(dex_subset, dose >10)
# # ^ shows high dex values which need to be manually changed - need to be * 1000.
# 
# medication_clean$dose <-
#   ifelse(medication_clean$coid_asse_id == "19157E 14782" & medication_clean$hours_through_day == 17,
#         as.numeric(medication_clean$dose) / 1000,
#         as.numeric(medication_clean$dose))
# 
# medication_clean$dose <-
#   ifelse(medication_clean$coid_asse_id == "56050E 1734",
#         as.numeric(medication_clean$dose) / 1000,
#         as.numeric(medication_clean$dose))
# 
# medication_clean$dose <-
#   ifelse(medication_clean$coid_asse_id == "59565E 16733" & medication_clean$medicine == "dexamethasone",
#         as.numeric(medication_clean$dose) / 1000,
#         as.numeric(medication_clean$dose))
# 
# medication_clean$dose <-
#   ifelse(medication_clean$coid_asse_id == "27380E 16997" & medication_clean$medicine == "dexamethasone",
#         as.numeric(medication_clean$dose) / 1000,
#         as.numeric(medication_clean$dose))	
# 
# medication_clean$dose <-
#   ifelse(medication_clean$coid_asse_id == "18021E 21449" & medication_clean$medicine == "dexamethasone",
#         as.numeric(medication_clean$dose) / 1000,
#         as.numeric(medication_clean$dose))

# 
# # once manual adjustments of dex values have been made, run these lines - 'dex_HIGH_values' should now be empty and max dex dose should be less than 10!
# dex_subset <- subset(medication_clean, medicine == "dexamethasone")
# dex_HIGH_values <- subset(dex_subset, dose >10)
# dex_HIGH_values
# max(dex_subset$dose, na.rm = T)
```

```{r : adding in HC equivalents}
# this table shows how many records of each medication are present (bare in mind one participant can have multiple records)
table(medication_clean$medicine)

medication_clean$HC_equivalent <- NA

prednisoloneratio <- 5
# dexamethasoneratio <- 80

medication_clean$HC_equivalent <- 
  ifelse(medication_clean$medicine == "hydrocortisone", medication_clean$dose, NA)

medication_clean$HC_equivalent <- 
  ifelse(medication_clean$medicine == "prednisolone", (as.numeric(medication_clean$dose) * prednisoloneratio), medication_clean$HC_equivalent)

# medication_clean$HC_equivalent <- 
#   ifelse(medication_clean$medicine == "dexamethasone", (as.numeric(medication_clean$dose) * dexamethasoneratio), medication_clean$HC_equivalent)

# let's double check the HC equivalent values seem sensible. You'll have a better idea than me of what is sensible here!
checkmedstats <- medication_clean %>%
  group_by(medicine) %>%
  summarise(mean_dose = mean(HC_equivalent, na.rm = TRUE),
            median_dose = median(HC_equivalent,na.rm= TRUE),
            sd_dose = sd(HC_equivalent, na.rm = TRUE),
            min_dose = min(HC_equivalent, na.rm = TRUE),
            max_dose = max(HC_equivalent, na.rm = TRUE)) %>%
  mutate_if(is.numeric, ~round(., 2))
```

BSA is present in 'participants' frame.
```{r : adding HC/bsa and fludro/bsa}
# I have used HC_equivalents in this HC per BSA calculation.
medication_clean$HC_per_bsa <- medication_clean$HC_equivalent / participantsnoduplicates$BSA...CAH.Longitudinal.Data

medication_clean$HC_per_bsa <- round(medication_clean$HC_per_bsa, digits = 2)

# Join fludo dose to medication_clean to use for getting fludro/bsa
# need to make new subset fludro frame
fludro$coid_asse_date <- paste(fludro$CO.ID, fludro$assessment_date)
fludro_subset <- select(fludro, c ("coid_asse_date", "fludrocortisone_dose"))
medication_clean <- left_join(medication_clean, fludro_subset, by = c ("coid_asse_date"))

medication_clean$fludro_per_bsa <- medication_clean$fludrocortisone_dose / participantsnoduplicates$BSA...CAH.Longitudinal.Data

medication_clean$fludro_per_bsa <- round(medication_clean$fludro_per_bsa, digits = 2)
```

Checking that there are no duplicated assessment ids for different dates (note: can have same asse id on same date)
```{r : checking duplicate assessment dates}
medication_date_check <- 
  medication_clean %>% 
  group_by(assessment_id) %>% 
  summarise(
    min_date = min(assessment_date),
    max_date = max(assessment_date))

medication_date_check$difference <- 
  medication_date_check$max_date - 
  medication_date_check$min_date

min(as.numeric(medication_date_check$difference))
max(as.numeric(medication_date_check$difference))
# ^ all should equal 0 days difference. This means that all dates within the same assessments are the same.
```
```{r : create new variable names to make joining data frames later easier}
medication_clean$meds_unit <- medication_clean$unit
medication_clean$GC_dose <- medication_clean$dose
```

```{r : sequence along entries}
medication_clean$assessment_entry <-
  ave(medication_clean$record_id,
      medication_clean$assessment_id,
      FUN = seq_along)
```

Check frequencies of entries to check for a single assessment having lots of entries (i.e. duplications) which may indicate erroneously duplicated entries
```{r}
table(medication_clean$assessment_entry)
```

```{r : making meds_wide}
medication_clean_1st_entry <- 
  medication_clean %>% 
  filter(assessment_entry==1)

medication_clean_2nd_entry <- 
  medication_clean %>% 
  filter(assessment_entry==2)

medication_clean_3rd_entry <- 
  medication_clean %>% 
  filter(assessment_entry==3)

medication_clean_4th_entry <- 
  medication_clean %>% 
  filter(assessment_entry==4)

medication_clean_5th_entry <- 
  medication_clean %>% 
  filter(assessment_entry==5)

medication_clean_6th_entry <- 
  medication_clean %>% 
  filter(assessment_entry==6)

# now we can get rid of the assessment entry column
# medication$assessment_entry <- NULL
medication_clean$assessment_entry <- NULL

medication_clean_1st_entry$assessment_entry <- NULL

medication_clean_2nd_entry$assessment_entry <- NULL

medication_clean_3rd_entry$assessment_entry <- NULL

medication_clean_4th_entry$assessment_entry <- NULL

medication_clean_5th_entry$assessment_entry <- NULL

medication_clean_6th_entry$assessment_entry <- NULL


#then add the appropriate suffix to each column in these frames to make them different before joining
colnames(medication_clean_1st_entry) <- 
  paste(colnames(medication_clean_1st_entry), 1, sep="_")

colnames(medication_clean_2nd_entry) <- 
  paste(colnames(medication_clean_2nd_entry), 2, sep="_")

colnames(medication_clean_3rd_entry) <- 
  paste(colnames(medication_clean_3rd_entry), 3, sep="_")

colnames(medication_clean_4th_entry) <- 
  paste(colnames(medication_clean_4th_entry),4, sep="_")

colnames(medication_clean_5th_entry) <- 
  paste(colnames(medication_clean_5th_entry), 5, sep="_")

colnames(medication_clean_6th_entry) <- 
  paste(colnames(medication_clean_6th_entry),6, sep="_")


medication_clean_1st_entry <- medication_clean_1st_entry %>%
  rename("record_id" = "record_id_1",
         "assessment_id" = "assessment_id_1",
         "meds_assessment_date" = "assessment_date_1")

medication_clean_2nd_entry <- medication_clean_2nd_entry %>%
  rename("record_id" = "record_id_2",
         "assessment_id" = "assessment_id_2",
         "meds_assessment_date" = "assessment_date_2")

medication_clean_3rd_entry <- medication_clean_3rd_entry %>%
  rename("record_id" = "record_id_3",
         "assessment_id" = "assessment_id_3",
         "meds_assessment_date" = "assessment_date_3")

medication_clean_4th_entry <- medication_clean_4th_entry %>%
  rename("record_id" = "record_id_4",
         "assessment_id" = "assessment_id_4",
         "meds_assessment_date" = "assessment_date_4")

medication_clean_5th_entry <- medication_clean_5th_entry %>%
  rename("record_id" = "record_id_5",
         "assessment_id" = "assessment_id_5",
         "meds_assessment_date" = "assessment_date_5")

medication_clean_6th_entry <- medication_clean_6th_entry %>%
  rename("record_id" = "record_id_6",
         "assessment_id" = "assessment_id_6",
         "meds_assessment_date" = "assessment_date_6")
```

```{r : joining widened med frames together}
meds_wide <- medication_clean_1st_entry %>%
  left_join(medication_clean_2nd_entry, by=c("record_id", "assessment_id", "meds_assessment_date")) %>%
  left_join(medication_clean_3rd_entry, by=c("record_id", "assessment_id", "meds_assessment_date")) %>%
  left_join(medication_clean_4th_entry, by=c("record_id", "assessment_id", "meds_assessment_date")) %>%
  left_join(medication_clean_5th_entry, by=c("record_id", "assessment_id", "meds_assessment_date")) %>%
  left_join(medication_clean_6th_entry, by=c("record_id", "assessment_id", "meds_assessment_date"))

# adding in single total medication
meds_all <- left_join(meds_wide, singletotalmedication, by = c("record_id", "assessment_id"))

write.csv(meds_wide, file = "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/meds_wide.csv", row.names = F, na = "")
```

Subset dataframes

```{r : subsetting meds_wide}
meds_wide_subset <- subset(meds_wide, select = c("centreName_1", "record_id", "assessment_id", "meds_assessment_date", "coid_asse_id_1", "coid_asse_date_1",
"medicine_1", "dose_1", "hours_through_day_1", "HC_equivalent_1", "HC_per_bsa_1", "fludrocortisone_dose_1", "fludro_per_bsa_1",
"medicine_2", "dose_2", "hours_through_day_2", "HC_equivalent_2", "HC_per_bsa_2", "fludrocortisone_dose_2", "fludro_per_bsa_2",
"medicine_3", "dose_3", "hours_through_day_3", "HC_equivalent_3", "HC_per_bsa_3", "fludrocortisone_dose_3", "fludro_per_bsa_3",
"medicine_4", "dose_4", "hours_through_day_4", "HC_equivalent_4", "HC_per_bsa_4", "fludrocortisone_dose_4", "fludro_per_bsa_4",
"medicine_5", "dose_5", "hours_through_day_5", "HC_equivalent_5", "HC_per_bsa_5", "fludrocortisone_dose_5", "fludro_per_bsa_5",
"medicine_6", "dose_6", "hours_through_day_6", "HC_equivalent_6", "HC_per_bsa_6", "fludrocortisone_dose_6", "fludro_per_bsa_6"))

meds_wide_subset <- meds_wide_subset %>%
  rename("coid_asse_date" = "coid_asse_date_1")

# removing all duplicated entries (based on coid_asse_date)
med_duplicates <- meds_wide_subset[duplicated(meds_wide_subset$coid_asse_date),]
med_entries_to_remove <- med_duplicates$coid_asse_date
meds_wide_subset <- subset(meds_wide_subset, !coid_asse_date %in% med_entries_to_remove)

# med_duplicates_check should now be empty
med_duplicates_check <- meds_wide_subset[duplicated(meds_wide_subset$coid_asse_date),]

write.csv(meds_wide_subset, file = "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/meds_wide_subset.csv", row.names = F, na = "")
```

***********************
Joining lab to participants
************************

```{r : making labs wide, include=FALSE}
# editing lab dataframe to use it here
labs[labs == "NULL"] <- NA

labsvalues <- subset(labs, select = -c(result, date_and_time))

labsvalues <- labsvalues %>%
  drop_na() %>%
  pivot_wider(names_from = "labs_type",
              values_from = "value")

labsinterp <- subset(labs, select = -c(value, date_and_time))
labsinterp <- labsinterp %>%
  drop_na() %>%
  pivot_wider(names_from = "labs_type",
              values_from = "result")

labs_wide <- left_join(labsvalues, labsinterp, by = c("record_id", "assessment_id", "assessment_date", "centreName"))

names(labs_wide) <- gsub(x = names(labs_wide), pattern = ".x",
                        replacement = ".value")
names(labs_wide) <- gsub(x = names(labs_wide), pattern = ".y",
                        replacement = ".interpretation")

labs_wide$coid_asse_date <- paste(labs_wide$record_id, labs_wide$assessment_date)
labs_wide$coid_asse_id <- paste(labs_wide$record_id, labs_wide$assessment_id)

# only interested in a subset of lab results - only want 17OHP and andostrodione
labs_wide_subset <- select(labs_wide, c("record_id", "assessment_date", "coid_asse_date", "ohp17.value", "ohp17.interpretation", "andostenedione.value", "andostenedione.interpretation"))

# removing all duplicated entries (based on coid_asse_date)
lab_duplicates <- labs_wide_subset[duplicated(labs_wide_subset$coid_asse_date),]
lab_entries_to_remove <- lab_duplicates$coid_asse_date
labs_wide_subset <- subset(labs_wide_subset, !coid_asse_date %in% lab_entries_to_remove)

# lab_duplicates_check should now be empty
lab_duplicates_check <- labs_wide_subset[duplicated(labs_wide_subset$coid_asse_date),]

labs_wide_subset_for_export <- apply(labs_wide_subset, 2, as.character)
write.csv(labs_wide_subset_for_export, file = "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/labs_wide_subset.csv", row.names = F, na = "")
```


~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
~~~~~~~~~~~~~~~~~~CLEAR ENVIRONMENT NOW~~~~~~~~~~~~~~~~~~
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

```{r : clear environment}
rm(list=ls())
```

Re-read these files back into cleaned environment
```{r : re-reading files in to clear environment}
participantsnoduplicates <- read.csv("C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/participantsnoduplicates.csv", header=T, na.strings="")
meds_wide_subset <- read.csv("C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/meds_wide_subset.csv", header=T, na.strings="")
labs_wide_subset <- read.csv("C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/labs_wide_subset.csv", header=T, na.strings="")
medsandae <- read.csv("C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/medsandae.csv", header=T, na.strings="")
```

```{r : making UK compiled data, include= FALSE}
# rename record id in participantsnoduplicates to permit joining simply
participantsnoduplicates <- participantsnoduplicates %>%
  rename("record_id" = "Register.ID...Record")

# join medsandae
I_CAH_UK_data <- left_join(participantsnoduplicates, medsandae, by=c("record_id", "coid_asse_date"))

I_CAH_UK_data$visit_date <- I_CAH_UK_data$Date...CAH.Longitudinal.Data
I_CAH_UK_data$Age_at_visit <- I_CAH_UK_data$Age.at.assessment
I_CAH_UK_data$BSA <- I_CAH_UK_data$BSA...CAH.Longitudinal.Data

# join meds_wide_subset
I_CAH_UK_data <- left_join(I_CAH_UK_data, meds_wide_subset, by = c("record_id", "coid_asse_date"))

# join labs_wide_subset
I_CAH_UK_data <- left_join(I_CAH_UK_data, labs_wide_subset, by = c("record_id", "coid_asse_date"))
```

```{r : checking duplications in I_CAH_UK_data}
# let's see which rows are duplications
# this data frame should be empty!
I_CAH_UK_dataduplications <- I_CAH_UK_data[duplicated(I_CAH_UK_data$coid_asse_date),]
```

```{r : writing final table - I_CAH_UK_data}
write.csv(I_CAH_UK_data, file = "C:/Users/md1rwe/Documents/R work/I-CAH UK practice/I-CAH-UK-practice/outputs/I_CAH_UK_data.csv", row.names = F, na = "")
```

